---
title: "Main Functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Main Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(demr)

dem_data <- load_data()
```

## Load the data

The `load_data()` function loads the democracy and representation dataset used in this package.

```{r}
dem_data <- load_data()
head(dem_data)
```

## Function 1: Plot democracy scores by region

The `plot_demscore()` function creates a violin plot showing the distribution of spatial democracy scores by region.

```{r}
plot_demscore("High")
```

## Function 2: Plot one region

The `plot_by_cont()` function creates a scatterplot for one selected region. It compares logged population proportion to spatial democracy score, with points colored by representation type.

```{r}
plot_by_cont(dem_data, "Europe")
```

## Function 3: Summarize by country

The `avg_table_country()` function condenses the data by country and calculates average values for spatial democracy, population proportion, and logged population proportion.

```{r}
avg_table_country(dem_data)
```

## Function 4: Run ANOVA by representation type

The `anova_rep_type()` function runs a one-way ANOVA to test whether average spatial democracy scores differ across representation types.

```{r}
anova_rep_type(dem_data)
```

A small p-value would suggest that average spatial democracy scores are not equal across all representation categories.













