---
title: "main-functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{main-functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(demr)
```


Function 1:

```{r}
plot_dem_score_cont(dem_data, continent, level)
```

This one is for a violin plot very similar to our Shiny output, which would be a violin plot with democracy index as the variable of interest, for a specified continent and desired level of representation.

Function 2:

```{r}
plot_by_cont(dem_data, continent)
```

This would be a similar one to the first, but we would give a continent and then output a scatterplot with representation level on the x axis and democracy index on the y axis.

Function 3:

```{r}
avg_table_country(dem_data, by_country= TRUE)
```

This final one would condense the data, by sorting the data by country and then taking averages of all of the democracy data over the years. 





























